Sound Automated Synthesis of Digital Controllers

### 2016-10-09 paper/paper.tex
Changes in Section 2

@@

\begin{mylemma}\cite{astrom1997computer}
%
The pulse transfer function $G(z)$ is a z-domain model that relates the
output sampled by a ADC and the digital input provided by ZOH.  It is
equivalent at the sample times ({\it i.e.}, $kT$ to the continuous transfer
function $G(s)$ driven by ZOH).  This pulse transfer function can be
computed as
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
For the sake of brevity, 
we will use only the notation $G(z)$ to represent the pulse transfer function.
%
\end{mylemma}
Since $G(z)$ is an approximation of $G(s)$ we introduce an error term caused during its calculation as $\Delta{G}_P$

@@

Consider the closed-loop sampled system in Figure~\ref{fig:sampledsystem},
where $C(z)$ is the digital controller model, whose control output signal is
quantized ($Q2$) and interpolated via a ZOH using digital-to-analog
converter (DAC).  The quantization occurs because the DAC resolution may be
different from the fixed point representation of the controller.  $G(s)$ is
the continuous-time model of the plant, from which output samples are taken
and quantized ($Q1$) by means of an analog-to-digital converter (ADC)
synchronized with the DAC.  Each quantizer ($Q1$ and $Q2$) will present some
contribution for the total quantization noise.
%    
\begin{figure*}[ht]
\centering

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
    \node[draw=none] (r) {$\tilde R(z)$};
%   \& \coordinate (aux0);
   \& \node[circle,add={-}{+}{}{}] (circle) {};
   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$\tilde e(z)$};
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Controller}] (cz) {{\sc C(z)}};
   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$\tilde U(z)$};

   \& complexnode/.pic={ 
      \node[rectangle,draw,
	minimum width=3cm,
	minimum height=1.6cm,
	label=\textbf{DAC},] (dac) {};
     \node[circle,add={}{+}{+}{},fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {};
     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
     \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc G(s)}};
   \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]gs)  {$U(s)$};
   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(s)$};
   \& complexnode/.pic={ 
     \node[rectangle,draw,
	minimum width=4cm,
	minimum height=1.6cm,
	label=\textbf{ADC},] (adc) {};
   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
   \coordinate (switch1) at ([xshift=-1cm]adc.center);
   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
   \& \coordinate (aux1);
   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
   \& \coordinate (aux3); 
   \&
   \&
   \& 
   \& 
   \& \coordinate (aux2);\\
  };

%% \begin{figure}[ht]
%% \centering
%% \includegraphics[width=\columnwidth]{figures/hsystembd.pdf}
%% \caption{Sampled system.}
%% \label{fig:sampledsystem}
%% \end{figure}

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
    \node[draw=none] (r) {$R(z)$};
%   \& \coordinate (aux0);
   \& \node[circle,add={-}{+}{}{}] (circle) {};
   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Controller}] (cz) {{\sc C(z)}};
   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc G(z)}};
   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};

%  \path[->] (v1) edge (q1.north);
%  \path[->] (v2) edge (q2.north);
  \path[->] (r) edge (circle.west);
  \path[->] (nu) edge (circle2.north);
  \path[->] (aux1) edge (yz);
  \path  
   (circle.east) edge (cz)
   (cz.east) edge (gs.west)
   (gs.east) edge (circle2.west)
   (circle2.east) edge (aux1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Sampled System. \label{fig:sampledsystem}}
\end{figure}

%
%

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
    \node[draw=none] (r) {$R(z)$};
%   \& \coordinate (aux0);
   \& \node[circle,add={-}{+}{}{}] (circle) {};
   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
   \& \coordinate (aux4);
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Controller}] (cz) {{\sc C(z)}};
   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc G(z)}};
   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
   \& \node[circle,add={+}{+}{}{}] (circle2) {};
%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
%   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
   \& \coordinate (aux1);
   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
   \& 
   \& \coordinate (aux5); 
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm] (deltag) {{\sc $\Delta G(z)$}};
   \&
   \& \coordinate (aux6);\\
   \& \coordinate (aux3); 
   \&
   \& 
   \& 
   \&
   \& \coordinate (aux2);\\
  };

%  \path[->] (v1) edge (q1.north);
%  \path[->] (v2) edge (q2.north);
  \path[->] (r) edge (circle.west);
%  \path[->] (nu) edge (circle2.north);
  \path[->] (aux1) edge (yz);
  \path  
   (aux4.north) edge (aux5.south)
   (aux5.east) edge (deltag.west)
   (deltag.east) edge (aux6.west)
   (aux6.south) edge (circle2.south)
   (circle.east) edge (cz)
   (cz.east) edge (gs.west)
   (gs.east) edge (circle2.west)
   (circle2.east) edge (aux1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Sampled System. \label{fig:sampledsystem}}
\end{figure}

>>>>

\textcolor{blue}{[IB: I'm proposing some changes in this section based on Alessandro's comments and trying to obtain a simpler and uniform notation.]}

@@

\begin{mylemma}\cite{astrom1997computer}
%
The pulse transfer function $G(z)$ is a z-domain model that relates the
output sampled by a ADC and the digital input provided by ZOH.  It is
equivalent at the sample times ({\it i.e.}, $kT$ to the continuous transfer
function $G(s)$ driven by ZOH).  This pulse transfer function can be
computed as
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
For the sake of brevity, 
we will use only the notation $G(z)$ to represent the pulse transfer function.
%
\end{mylemma}

\textcolor{blue}{
Although the pulse transfer function $G(z)$ represents adequately $G(s)$ domain, the model $G(z)$ may not be accurate and some uncertainties may not be covered by that model. These uncertainties may be parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
\begin{equation}
\hat{G}(z)=G(z)+\Delta G(z),
\end{equation}
that may be represented by the following transfer function:
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}}.
\end{equation}}

\textcolor{blue}{
The vector of parametric uncertainties  $\Delta{p}$ for $G(z)$ is defined by:
\begin{equation}
\Delta{p}=\begin{bmatrix}
\hat{b_{0}} - b_{0}\\
\hat{b_{1}} - b_{1}\\
\vdots \\
\hat{b}_{M_G} - b_{M_{G}}\\
\hat{a_{0}} - a_{0}\\
\hat{a_{1}} - a_{1}\\
\vdots\\
\hat{a}_{N_G} - a_{N_{G}}\\
\end{bmatrix}.
\end{equation}}

\textcolor{blue}{
A typical hybrid system is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$, $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.}

\begin{figure*}[htb]
\centering

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
    \node[draw=none] (r) {$R(z)$};
%   \& \coordinate (aux0);
   \& \node[circle,add={-}{+}{}{}] (circle) {};
   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Controller}] (cz) {{\sc C(z)}};
   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};

   \& complexnode/.pic={ 
      \node[rectangle,draw,
	minimum width=3cm,
	minimum height=1.6cm,
	label=\textbf{DAC},] (dac) {};
     \node[circle,add={}{+}{+}{},fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {};
     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
     \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc $G(s) + \Delta G(s)$}};
   \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]gs)  {$U(s)$};
   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(s)$};
   \& complexnode/.pic={ 
     \node[rectangle,draw,
	minimum width=4cm,
	minimum height=1.6cm,
	label=\textbf{ADC},] (adc) {};
   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
   \coordinate (switch1) at ([xshift=-1cm]adc.center);
   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
   \& \coordinate (aux1);
   \& \node[draw=none] (yz) {$\hat{Y}(z)$};\\
   \& \coordinate (aux3); 
   \&
   \&
   \& 
   \& 
   \& \coordinate (aux2);\\
  };

\textcolor{blue}{
The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta G_{P}(z)$ and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is represented as an additive measurement noise $\nu(z)$.}

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
    \node[draw=none] (r) {$R(z)$};
%   \& \coordinate (aux0);
   \& \node[circle,add={-}{+}{}{}] (circle) {};
   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Controller}] (cz) {{\sc C(z)}};
   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc $G(z) + \Delta G_{P}(z)$}};
   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};

%  \path[->] (v1) edge (q1.north);
%  \path[->] (v2) edge (q2.north);
  \path[->] (r) edge (circle.west);
  \path[->] (nu) edge (circle2.north);
  \path[->] (aux1) edge (yz);
  \path  
   (circle.east) edge (cz)
   (cz.east) edge (gs.west)
   (gs.east) edge (circle2.west)
   (circle2.east) edge (aux1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Digital system equivalent to ~\ref{fig:sampledsystem}. \label{fig:digsystem1}}
\end{figure}

%
\textcolor{blue}{
In figure~\ref{fig:digsystem1}, two sources of uncertainties are considered: parametric uncertainties related to modeling errors, and uncertainties introduced by quantisations in sampling and holding process, {\it i.e.} ADC and DAC conversions. Assuming linearity and independence between these sources, the uncertain model may be rewritten as follows:
\begin{equation}
\hat{G}(z)=G(z)+\Delta G_{P}(z)+\Delta G_{Q}(z),
\end{equation}
where $\Delta G_{P}(z)$ is the term that corresponds to the parametric uncertainties and $\Delta G_{Q}(z)$ is the term that reflects the quantisation effects on the plant model. Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.}

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
  %
	\& 
	\&
	\& \coordinate (aux7); 
	\& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm] (deltag2) {{\sc $\Delta G_{Q}(z)$}};
	\& \coordinate (aux8);\\
    \node[draw=none] (r) {$R(z)$};
%   \& \coordinate (aux0);
   \& \node[circle,add={-}{+}{}{}] (circle) {};
   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Controller}] (cz) {{\sc C(z)}};
   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
   \& \coordinate (aux4);
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc G(z)}};
   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
   \& \node[circle,add={+}{+}{+}{}] (circle2) {};
%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
%   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
   \& \coordinate (aux1);
   \& \node[draw=none] (yz) {$\hat{Y}(z)$};\\
   \& 
   \&
   \& \coordinate (aux5); 
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm] (deltag) {{\sc $\Delta G_{P}(z)$}};
   \& \coordinate (aux6);\\
   \& \coordinate (aux3); 
   \&
   \& 
   \& 
   \&
   \& \coordinate (aux2);\\
  };

%  \path[->] (v1) edge (q1.north);
%  \path[->] (v2) edge (q2.north);
  \path[->] (r) edge (circle.west);
%  \path[->] (nu) edge (circle2.north);
  \path[->] (aux1) edge (yz);
  \path  
   (aux4.north) edge (aux5.south)
   (aux4.north) edge (aux7.south)
   (aux5.east) edge (deltag.west)
   (aux7.east) edge (deltag2.west)
   (deltag.east) edge (aux6.west)
   (deltag2.east) edge (aux8.west)
   (circle.east) edge (cz)
   (cz.east) edge (gs.west)
   (circle2.east) edge (aux1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->] (aux8.south) edge (circle2.north); 
  \path[->] (aux6.south) edge (circle2.south);
  \path[->] (gs.east) edge (circle2.west);
  \path[->] (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Digital system with additive uncertainties $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$. \label{fig:digsystem2}}
\end{figure}

\textcolor{blue}{[IB: I propose to exchange the following paragraphs by the previous blue]}

Since $G(z)$ is an approximation of $G(s)$ we introduce an error term caused during its calculation as $\Delta{G}_P$

@@

Consider the closed-loop sampled system in Figure~\ref{fig:sampledsystem},
where $C(z)$ is the digital controller model, whose control output signal is
quantized ($Q2$) and interpolated via a ZOH using digital-to-analog
converter (DAC).  The quantization occurs because the DAC resolution may be
different from the fixed point representation of the controller.  $G(s)$ is
the continuous-time model of the plant, from which output samples are taken
and quantized ($Q1$) by means of an analog-to-digital converter (ADC)
synchronized with the DAC.  Each quantizer ($Q1$ and $Q2$) will present some
contribution for the total quantization noise.
%    
%\begin{figure*}[ht]
%\centering
%
%\tikzset{add/.style n args={4}{
%    minimum width=6mm,
%    path picture={
%        \draw[circle] 
%            (path picture bounding box.south east) -- (path picture bounding box.north west)
%            (path picture bounding box.south west) -- (path picture bounding box.north east);
%        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
%        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
%        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
%        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
%        }
%    }
% }
%
%\resizebox{.8\textwidth}{!}{
% \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
%     semithick, initial text=, ampersand replacement=\&,]
%
%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
%    \node[draw=none] (r) {$\tilde R(z)$};
%%   \& \coordinate (aux0);
%   \& \node[circle,add={-}{+}{}{}] (circle) {};
%   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$\tilde e(z)$};
%   \& \node[rectangle,draw,
%	minimum width=1cm,
%	minimum height=1cm,
%        label=\textbf{Controller}] (cz) {{\sc C(z)}};
%   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$\tilde U(z)$};
%     
%   \& complexnode/.pic={ 
%      \node[rectangle,draw,
%	minimum width=3cm,
%	minimum height=1.6cm,
%	label=\textbf{DAC},] (dac) {};
%     \node[circle,add={}{+}{+}{},fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {};
%     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
%     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
%     \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}
%   \& \node[rectangle,draw,
%	minimum width=1cm,
%	minimum height=1cm,
%        label=\textbf{Plant}] (gs) {{\sc G(s)}};
%   \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]gs)  {$U(s)$};
%   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(s)$};
%   \& complexnode/.pic={ 
%     \node[rectangle,draw,
%	minimum width=4cm,
%	minimum height=1.6cm,
%	label=\textbf{ADC},] (adc) {};
%   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
%   \coordinate (switch1) at ([xshift=-1cm]adc.center);
%   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
%   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
%     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
%   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
%   \& \coordinate (aux1);
%   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
%   \& \coordinate (aux3); 
%   \&
%   \&
%   \& 
%   \& 
%   \& \coordinate (aux2);\\
%  };
%
%
%  \path[->] (v1) edge (q1.north);
%  \path[->] (v2) edge (q2.north);
%  \path[->] (r) edge (circle.west);
%  \path[->] (aux1) edge (yz);
%  \path  
%   (circle.east) edge (cz)
%   (cz.east) edge (q2.west)
%   (q2.east) edge (zoh.west)
%   (zoh.east) edge (gs.west)
%   (switch2) edge (q1.west)
%   (q1.east) edge (aux1.west)
%   (gs.east) edge (switch1.west)
%   (aux1.south) edge (aux2.north)
%   (aux2.west) edge (aux3.east); 
%  \path[->]  (aux3.north) edge (circle.south);
% \end{tikzpicture}
%}
% \caption{Sampled System. \label{fig:sampledsystem}}
%\end{figure*}
%
%%% \begin{figure}[ht]
%%% \centering
%%% \includegraphics[width=\columnwidth]{figures/hsystembd.pdf}
%%% \caption{Sampled system.}
%%% \label{fig:sampledsystem}
%%% \end{figure}
%
%
%\begin{figure}[ht]
%\centering
%
%\tikzset{add/.style n args={4}{
%    minimum width=6mm,
%    path picture={
%        \draw[circle] 
%            (path picture bounding box.south east) -- (path picture bounding box.north west)
%            (path picture bounding box.south west) -- (path picture bounding box.north east);
%        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
%        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
%        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
%        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
%        }
%    }
% }
%
%\resizebox{.5\textwidth}{!}{
% \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
%     semithick, initial text=, ampersand replacement=\&,]
%
%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
%    \node[draw=none] (r) {$R(z)$};
%%   \& \coordinate (aux0);
%   \& \node[circle,add={-}{+}{}{}] (circle) {};
%   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
%   \& \node[rectangle,draw,
%	minimum width=1cm,
%	minimum height=1cm,
%        label=\textbf{Controller}] (cz) {{\sc C(z)}};
%   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
%   \& \node[rectangle,draw,
%	minimum width=1cm,
%	minimum height=1cm,
%        label=\textbf{Plant}] (gs) {{\sc G(z)}};
%   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
%
%   \& \node[circle,add={}{+}{+}{}] (circle2) {};
%%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
%   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
%   \& \coordinate (aux1);
%   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
%   \& \coordinate (aux3); 
%   \&
%   \& 
%   \& 
%   \& \coordinate (aux2);\\
%  };
%
%
%%  \path[->] (v1) edge (q1.north);
%%  \path[->] (v2) edge (q2.north);
%  \path[->] (r) edge (circle.west);
%  \path[->] (nu) edge (circle2.north);
%  \path[->] (aux1) edge (yz);
%  \path  
%   (circle.east) edge (cz)
%   (cz.east) edge (gs.west)
%   (gs.east) edge (circle2.west)
%   (circle2.east) edge (aux1.west)
%   (aux1.south) edge (aux2.north)
%   (aux2.west) edge (aux3.east); 
%  \path[->]  (aux3.north) edge (circle.south);
% \end{tikzpicture}
%}
% \caption{Sampled System. \label{fig:sampledsystem}}
%\end{figure}
%
%%
%%
%
%\begin{figure}[ht]
%\centering
%
%\tikzset{add/.style n args={4}{
%    minimum width=6mm,
%    path picture={
%        \draw[circle] 
%            (path picture bounding box.south east) -- (path picture bounding box.north west)
%            (path picture bounding box.south west) -- (path picture bounding box.north east);
%        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
%        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
%        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
%        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
%        }
%    }
% }
%
%\resizebox{.5\textwidth}{!}{
% \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
%     semithick, initial text=, ampersand replacement=\&,]
%
%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
%    \node[draw=none] (r) {$R(z)$};
%%   \& \coordinate (aux0);
%   \& \node[circle,add={-}{+}{}{}] (circle) {};
%   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
%   \& \coordinate (aux4);
%   \& \node[rectangle,draw,
%	minimum width=1cm,
%	minimum height=1cm,
%        label=\textbf{Controller}] (cz) {{\sc C(z)}};
%   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
%   \& \node[rectangle,draw,
%	minimum width=1cm,
%	minimum height=1cm,
%        label=\textbf{Plant}] (gs) {{\sc G(z)}};
%   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
%   \& \node[circle,add={+}{+}{}{}] (circle2) {};
%%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
%%   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
%   \& \coordinate (aux1);
%   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
%   \& 
%   \& \coordinate (aux5); 
%   \& \node[rectangle,draw,
%	minimum width=1cm,
%	minimum height=1cm] (deltag) {{\sc $\Delta G(z)$}};
%   \&
%   \& \coordinate (aux6);\\
%   \& \coordinate (aux3); 
%   \&
%   \& 
%   \& 
%   \&
%   \& \coordinate (aux2);\\
%  };
%
%
%%  \path[->] (v1) edge (q1.north);
%%  \path[->] (v2) edge (q2.north);
%  \path[->] (r) edge (circle.west);
%%  \path[->] (nu) edge (circle2.north);
%  \path[->] (aux1) edge (yz);
%  \path  
%   (aux4.north) edge (aux5.south)
%   (aux5.east) edge (deltag.west)
%   (deltag.east) edge (aux6.west)
%   (aux6.south) edge (circle2.south)
%   (circle.east) edge (cz)
%   (cz.east) edge (gs.west)
%   (gs.east) edge (circle2.west)
%   (circle2.east) edge (aux1.west)
%   (aux1.south) edge (aux2.north)
%   (aux2.west) edge (aux3.east); 
%  \path[->]  (aux3.north) edge (circle.south);
% \end{tikzpicture}
%}
% \caption{Sampled System. \label{fig:sampledsystem}}
%\end{figure}
